Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-11-09 analysis/paper/paper.Rmd
typo

We hypothesize that increased densitied of piscivorous predators in the Deadwater Slough area may explain the reduced survival (or apparent survival) observed for juvenile Chinook Salmon [@Ackerman2018] and Sockeye Salmon [@Axel2015]. In this study, we estimated the abundance of a piscivorous fish predator population in the Deadwater Slough and their potential impacts to juvenile salmon emigrants, focusing on DSR and NRR Chinook Salmon. Our objectives for the study were four-fold:

>>>>

We hypothesize that increased densities of piscivorous predators in the Deadwater Slough area may explain the reduced survival (or apparent survival) observed for juvenile Chinook Salmon [@Ackerman2018] and Sockeye Salmon [@Axel2015]. In this study, we estimated the abundance of a piscivorous fish predator population in the Deadwater Slough and their potential impacts to juvenile salmon emigrants, focusing on DSR and NRR Chinook Salmon. Our objectives for the study were four-fold:
